### 2019-05-11 ex1/ex1.tex
Minor rewording/typos

Fig.~\ref{fig:classes} shows an excerpt of an solution ARX finds for $k=3$. Some of the equivalence classes indeed assume the desired size of 3, while others are substantially larger.

>>>>

Fig.~\ref{fig:classes} shows an excerpt of a solution ARX finds for $k=3$. Some of the equivalence classes indeed assume the desired minimum size of 3, while others are substantially larger.
